---
title: "survey-results"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{survey-results}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  fig.width = 7,
  fig.height = 4.5,
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tidyverse)
library(stargazer)
library(multiwayvcov)
library(here)
library(multcomp)
library(mmtalent)
df <- prepare_data(mmtalent_df, populationweights2016)
```

# Graphs on attitudes and belief
To have the main result on attitudes and belief, we would like to have aggregate patterns 
before going into the individual level data.
```{r}
attitude_dt <- df %>%  
  mutate(AL=luck_fair,
         AT=talent_fair,
         AE=effort_fair,
         CL=luck_control,
         CT=talent_control,
         CE=effort_control) %>%
  dplyr::select(AL, AT, AE, CL, CT, CE, treatment, left, wgt) %>%
  gather(key = "outcome", value="value", AL, AT, AE, CL, CT, CE)
```

Now for creating the first graph: unconditional on political position:
```{r}
attitude_dt %>%
  mutate(outcometype = factor( ifelse(outcome %in% c("AL","AT", "AE"),"Attitude (unfairness)", "Belief on control")),
         f = fct_collapse(outcome,
                        Luck = c("AL","CL"),
                        Talent = c("AT","CT"),
                        Effort = c("AE", "CE")),
         fo = fct_relevel(f, c("Luck", "Talent", "Effort"))) %>%
  group_by(outcometype, fo, outcome) %>% summarize(m = weighted.mean(value, wgt), se = sd(value)/sqrt(n())) %>%
  ggplot(aes(x=fo, y=m)) +
  geom_bar(stat="identity") + facet_grid(.~ outcometype) + 
  geom_errorbar(aes(ymin=m-se, ymax=m+se), width=0.2) + 
  xlab("Factor considered") + ylab("Mean outcome \u00B1 s.e.m.") +
  theme_bw()
ggsave(here::here("graphs","attitudes_beliefs.pdf"))
```

Now, interacting with political position:
```{r}
attitude_dt %>%
  mutate(outcometype = factor( ifelse(outcome %in% c("AL","AT", "AE"),"Attitude (unfairness)", "Belief on control")),
         f = fct_collapse(outcome,
                        Luck = c("AL","CL"),
                        Talent = c("AT","CT"),
                        Effort = c("AE", "CE")),
         fo = fct_relevel(f, c("Luck", "Talent", "Effort")),
         left_description = c("Right", "Left")[left+1]) %>%
  group_by(outcometype, left_description, fo, outcome) %>% summarize(m = weighted.mean(value, wgt), se = sd(value)/sqrt(n()))  %>%
  ggplot(aes(x=fo, y=m)) +
  geom_bar(stat="identity") + facet_grid(left_description ~ outcometype) + 
  geom_errorbar(aes(ymin=m-se, ymax=m+se), width=0.2) + 
  xlab("Factor considered") + ylab("Mean outcome \u00B1 s.e.m.") +
  theme_bw()
ggsave(here::here("graphs","attitudes_beliefs_pol.pdf"))
```

# Regression table
We want to put attitudes on the left hand side and try to
explain it by the type of attitude and the perception of control
in the situation.

Now, we need to turn the data around a bit first:
```{r}
subjectives_dt <- df  %>% 
  mutate(AL=luck_fair,
         AT=talent_fair,
         AE=effort_fair,
         CL=luck_control,
         CT=talent_control,
         CE=effort_control,
         id = row_number()) %>%
  dplyr::select(AL, AT, AE, CL, CT, CE, treatment, gender, age, left, income_category, edu_category, id, wgt) %>%
  gather(key="key", value="y", AL, AT, AE, CL, CT, CE) %>%
  mutate(key = factor(key),
         fct = fct_collapse(key,
                            luck = c("AL","CL"),
                            talent = c("AT", "CT"),
                            effort = c("AE", "CE")),
         outcome = fct_collapse(key,
                                attitude = c("AL", "AT", "AE"),
                                controlbelief = c("CL","CT","CE"))) %>% 
  dplyr::select(-key) %>%
  spread( key = outcome, value=y) %>%
  mutate(Luck = 1.*( fct=="luck"), 
         Effort = 1.*(fct=="effort"), 
         Talent = 1.*(fct=="talent"))
subjectives_dt %>% sample_n(3) 
```

Now, it should be possible to run the regression 
$$ A_{i,t} = \beta_0 + \beta_1 B_{i,t} + \beta_2 X_i +  \phi_t + \epsilon_{i,t}, $$
where $i$ index the individual, and $t\in\{ \mathrm{effort}, \mathrm{talent}, \mathrm{luck}\}$, 
$A_{i,t}\in[0,10]$ is the fairness attitude, $B_{i,t}\in[0,10]$ is the control belief, 
$X_i$ is a set of individual controls, and $\phi_t$ is a set of fixed effect for each factor.

```{r}
AB1 <- lm( attitude ~ Talent + Effort, data=subjectives_dt, weights=wgt)
AB2 <- lm( attitude ~ Talent + Effort + controlbelief, data=subjectives_dt, weights=wgt)

AB3 <- lm( attitude ~ Talent + Effort +
             age + left + as.factor(income_category) + as.factor(edu_category) + as.factor(gender), data=subjectives_dt, weights=wgt)
AB4 <- lm( attitude ~ Talent + Effort + controlbelief + 
             age + left + as.factor(income_category) + as.factor(edu_category) + as.factor(gender), data=subjectives_dt, weights=wgt)
subjectives_left <- subjectives_dt %>% filter(left==1)
subjectives_right <- subjectives_dt %>% filter(left!=1)

AB5 <- lm( attitude ~ Talent + Effort + controlbelief + 
             age + as.factor(income_category) + as.factor(edu_category) + as.factor(gender), data = subjectives_left, weights=wgt)
AB6 <- lm( attitude ~ Talent + Effort + controlbelief + 
             age + as.factor(income_category) + as.factor(edu_category) + as.factor(gender), data = subjectives_right, weights=wgt)

stargazer( AB1, AB2, AB3, AB4, AB5, AB6,
           se = list(sqrt(diag(cluster.vcov(AB1, cluster=subjectives_dt$id))),
                     sqrt(diag(cluster.vcov(AB2, cluster=subjectives_dt$id))),
                     sqrt(diag(cluster.vcov(AB3, cluster=subjectives_dt$id))),
                     sqrt(diag(cluster.vcov(AB4, cluster=subjectives_dt$id))),
                     sqrt(diag(cluster.vcov(AB5, cluster=subjectives_left$id))),
                     sqrt(diag(cluster.vcov(AB6, cluster=subjectives_right$id)))),
           style="aer", type="text", keep.stat=c("rsq", "n"),
           column.labels=c("All participants", "Left-wing", "Non-left"),
           column.separate=c(4,1,1))
```



# Are there treatment effects on attitudes?
The survey came after the experiment.
Are there any treatment effect on the survey outcomes? We test for joint significance of the treatment
effects for each of the 6 outcomes.
```{r}
A1 <- lm(luck_fair ~ treatment, data = df)
A1w <- glht(A1, linfct= c("`treatmentEx Ante Personal` = 0",
                          "`treatmentEx Post Personal` = 0",
                          "`treatmentEx Post Impersonal` = 0"))
A2 <- lm(talent_fair ~ treatment, data = df)
A2w <- glht(A2, linfct= c("`treatmentEx Ante Personal` = 0",
                          "`treatmentEx Post Personal` = 0",
                          "`treatmentEx Post Impersonal` = 0"))
A3 <- lm(effort_fair ~ treatment, data = df)
A3w <- glht(A3, linfct= c("`treatmentEx Ante Personal` = 0",
                          "`treatmentEx Post Personal` = 0",
                          "`treatmentEx Post Impersonal` = 0"))
B1 <- lm(luck_control ~ treatment, data = df)
B1w <- glht(B1, linfct= c("`treatmentEx Ante Personal` = 0",
                          "`treatmentEx Post Personal` = 0",
                          "`treatmentEx Post Impersonal` = 0"))
B2 <- lm(talent_control ~ treatment, data = df)
B2w <- glht(B2, linfct= c("`treatmentEx Ante Personal` = 0",
                          "`treatmentEx Post Personal` = 0",
                          "`treatmentEx Post Impersonal` = 0"))
B3 <- lm(effort_control ~ treatment, data = df)
B3w <- glht(B3, linfct= c("`treatmentEx Ante Personal` = 0",
                          "`treatmentEx Post Personal` = 0",
                          "`treatmentEx Post Impersonal` = 0"))

wrow <- c("Joint p-value on treatment:", 
          sprintf("%4.3f", summary(A1w)$test$pvalue[1]),
          sprintf("%4.3f", summary(A2w)$test$pvalue[1]),
          sprintf("%4.3f", summary(A3w)$test$pvalue[1]),
          sprintf("%4.3f", summary(B1w)$test$pvalue[1]),
          sprintf("%4.3f", summary(B2w)$test$pvalue[1]),
          sprintf("%4.3f", summary(B3w)$test$pvalue[1]))

stargazer(A1, A2, A3, B1, B2, B3,
          style="aer", type="text", add.lines=list(wrow),
          keep.stat=c("n","rsq"))
```

We see that 3 out of 18 treatment effects are significant at the 10% level, which is not surprising
even under the null of no true effect.
